Atomify - a live LAMMPS visualizer

### 2016-10-10 ms.tex
Wrote more introduction

\documentclass[aps,pre,twocolumn,letterpaper,floatfix,showpacs]{revtex4}
\usepackage{graphicx} 
\usepackage{amsmath,amssymb,amsfonts} 
\usepackage{mathtools}
\usepackage{pdfpages}
\usepackage{afterpage}
\usepackage[hidelinks]{hyperref} 
\usepackage{epstopdf}
\begin{document}
\title{Atomify - a live LAMMPS visualizer}
\author{Anders Hafreager$^1$}
\author{Svenn-Arne Dragly$^{1}$} 
\author{Anders Malthe-S\o renssen$^1$}
\affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
\date{\today}

@@

When

@@

\subsection{Future work}
All parts of Atomify can easily be ported to the web using WebGL and Emscripten.

>>>>

\documentclass[aps,pre,twocolumn,letterpaper,floatfix]{revtex4}
\usepackage{graphicx} 
\usepackage{amsmath,amssymb,amsfonts} 
\usepackage{mathtools}
\usepackage{pdfpages}
\usepackage{afterpage}
\usepackage[hidelinks]{hyperref} 
\usepackage{epstopdf}
\begin{document}
\title{Atomify - a live LAMMPS visualizer}
\author{Anders Hafreager$^1$}
\author{Svenn-Arne Dragly$^{1}$} 
\author{Anders Malthe-S\o renssen$^1$}
\affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
\date{\today}

@@

The work in this paper is focused on LAMMPS. Although the software is well-documented and enables the user to perform advanced simulations, it can be a demanding job to learn how to use it well. A LAMMPS simulation is defined by a series of commands which are executed one by one. Physical quantities such as energy, temperature and stress can be measured by adding \textit{computes}. These can in turn be saved to file for plotting and further analysis. Particle trajectories can be saved to a file and visualized by tools such as VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}. The lack of an intuitive GUI and visualization \footnote{which are listed in the non-features list on the web page: \url{http://lammps.sandia.gov/non_features.html}} makes the workflow somewhat complicated.

Atomify solves this problem by combining the script editing, simulating and visualization into one single application. It uses LAMMPS as a library and executes commands one by one. A synchronization step copies the relevant information from LAMMPS to the GPU for visualization and data plotting.

@@

\subsection{Future work}
Atomify is far from finished. 
A web version of Atomify is in development. 
All parts of Atomify can easily be ported to the web using WebGL and Emscripten.
